Order Preserving Encryption Schemes: \\ Preventing the Leakage of Distribution\\ 6.857 Final Paper \\ Hrishikesh Joshi, Max Kolysh, Mari Miyachi, John Wang

### 2013-05-07 paper.tex
Working on the paper.

When the client attempts to query for $x$, he must perform a range query for $[x, x+1)$ on the server.

>>>>

Inserting in this scheme is simple, since nothing really has to be changed from Raluca et al (2013)'s mOPE scheme. The client will take the value $x$ to insert, create $x'$, then encrypt $x'$ to obtain a ciphertext. Inserting this ciphertext will involve moving down the server's binary search tree. The insertion process is started by the client acquiring the root node. The client then checks to see if $x'$ is larger or smaller than the root's decrypted value. This informs the client as to the direction in which it should move. Once it arrives at a leaf node, the client will insert the new ciphertext in the correct direction.

\begin{figure}
\lstset{language=Python}
\begin{lstlisting}
  TODO: Insert the insertion pseudocode here.
\end{lstlisting}
\caption{Pseudocode for the Insertion Algorithm}
\label{insertion_figure}
\end{figure}

Querying, however, gets more difficult, and the next section will discuss how the client can query for some value $y$.
